\vspace{-1.5em} \bf A general and efficient representation of ancestral recombination graphs

### 2024-04-17 paper.tex
Add Korfman ref
Closes #454

The \texttt{tskit} library is a liberally
licensed open source toolkit that provides a comprehensive suite
of tools for working with gARGs (encoded as a succinct tree sequence).
Based on core functionality written
in C, it provides interfaces in C, Python and Rust.
Tskit is mature software, widely used in population genetics, and
has been incorporated into numerous downstream
applications~\citep[e.g.,][]{haller2019slim,speidel2019method,
adrion2020community,
terasaki2021geonomics,
baumdicker2021efficient,
fan2022genealogical,
guo2022recombination,
korfmann2022weak,
mahmoudi2022bayesian,
petr2023slendr,
rasmussen2022espalier,
zhang2023biobank,
nowbandegani2023extremely,
ignatieva2023distribution,
fan2023likelihood,
tsambos2023link,
tagami2024tstrait}.
The technical details of \texttt{tskit}, and how it provides an
efficient and portable platform for ARG-based analysis, are beyond
the scope of this manuscript.
% In the interest of avoiding confusion, however, we list a
% few minor details in which the formal details of gARGs
% provided in Section~\ref{sec-gARG} differ from their practical implementation in
% \texttt{tskit}.
% Firstly, ``edges'' in tree sequence terminology would perhaps be better
% described as ``edge-intervals'', as each describes a single contiguous
% interval of genome inheritance between a pair of nodes.
% This denormalisation of the gARG data model is for efficiency purposes.
% Secondly, zero- rather than one-based indexing is used for
% nodes in ARGs and oriented trees; consequently  $-1$ is used to denote the presence of
% roots (rather than $0$ as used here for notational simplicity).

>>>>

The \texttt{tskit} library is a liberally
licensed open source toolkit that provides a comprehensive suite
of tools for working with gARGs (encoded as a succinct tree sequence).
Based on core functionality written
in C, it provides interfaces in C, Python and Rust.
Tskit is mature software, widely used in population genetics, and
has been incorporated into numerous downstream
applications~\citep[e.g.,][]{haller2019slim,speidel2019method,
adrion2020community,
terasaki2021geonomics,
baumdicker2021efficient,
fan2022genealogical,
guo2022recombination,
korfmann2022weak,
mahmoudi2022bayesian,
petr2023slendr,
rasmussen2022espalier,
zhang2023biobank,
nowbandegani2023extremely,
ignatieva2023distribution,
fan2023likelihood,
tsambos2023link,
tagami2024tstrait,
korfmann2024simultaneous}.
The technical details of \texttt{tskit}, and how it provides an
efficient and portable platform for ARG-based analysis, are beyond
the scope of this manuscript.
% In the interest of avoiding confusion, however, we list a
% few minor details in which the formal details of gARGs
% provided in Section~\ref{sec-gARG} differ from their practical implementation in
% \texttt{tskit}.
% Firstly, ``edges'' in tree sequence terminology would perhaps be better
% described as ``edge-intervals'', as each describes a single contiguous
% interval of genome inheritance between a pair of nodes.
% This denormalisation of the gARG data model is for efficiency purposes.
% Secondly, zero- rather than one-based indexing is used for
% nodes in ARGs and oriented trees; consequently  $-1$ is used to denote the presence of
% roots (rather than $0$ as used here for notational simplicity).
